Text as Policy: \\ Measuring Policy Similarity through Bill Text Reuse

### 2016-02-13 manuscript/text_reuse.tex
updating policy similarity

\setlength{\parindent}{0.0in}
\setlength{\parskip}{1ex plus 0.5ex minus 0.2ex}
\mmddyyyydate
\doublespacing
\externaldocument{tables/ideology_regs.tex}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

Before we describe the algorithm we use for detecting text re-use, and validate that algorithm, we should clearly define the latent variable we seek to measure through the assessment of text overlap. The latent variable that we argue below is measured effectively through text re-use is {\em policy similarity}. The text in legislation is an aggregate representation of the dimensions underlying the policies proposed therein. These dimensions include the domain of the policy, the ideological position enacted by the policy, the level of specificity in the policy enactment, and several other salient features of policy that are communicated through the text in legislation. We do not claim that the re-use of text can be used to measure these dimensions in a specific, disaggregated way. Rather, text re-use serves as a summary measure of similarity across all relevant policy dimensions represented in legislative text.

@@

In past research on policy adoption, studies have varied in terms of the degrees of similarity between policies

@@

\begin{table}[ht!]
\centering
\caption{My caption}
\label{my-label}
\begin{tabular}{lll}
               & alignment & no alignment \\
not same table & 11        & 232287       \\
same table     & 3083      & 20639       
\end{tabular}
\end{table}

>>>>

\setlength{\parindent}{0.0in}
\setlength{\parskip}{1ex plus 0.5ex minus 0.2ex}
\mmddyyyydate
\doublespacing
\externaldocument{tables/ideology_regs.tex}
\externaldocument{tables/ncsl_crosstab.tex}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

Before we describe the algorithm we use for detecting text re-use, and validate that algorithm, we should clearly define the latent variable we seek to measure through the assessment of text overlap. The latent variable that we argue below is measured effectively through text re-use is {\em policy similarity}. The text in legislation is an aggregate representation of the dimensions underlying the policies proposed therein. These dimensions include the domain of the policy, the ideological position enacted by the policy, the level of specificity in the policy enactment, and several other salient features of policy that are communicated through the text in legislation. We do not claim that the re-use of text can be used to measure these dimensions in a specific, disaggregated way. Rather, text re-use serves as a summary measure of similarity across all relevant policy dimensions represented in legislative text. With reference to existing literature, we show that studies of policy adoption and diffusion have typically focused on classes of similar policies, rather than looking for the adoption of {\em equivalent} policies.

@@

Drawing upon this general concept of similarity, we derive three empirical expectations regarding the behavior of text re-use as an effective measure of policy similarity. These will serve as validity tests going forward.

@@

\input{tables/ncsl_crosstab.tex}
